%-------------------------
% Modified from a resume by  Sourabh Bajaj
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\uref}[1]{\href{#1}{#1}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{\extracolsep{1em}}l}
  \textbf{\href{https://matklad.github.io/}{\Large Aleksey Kladov}} & Email :& \href{mailto:aleksey.kladov@gmail.com}{aleksey.kladov@gmail.com}\\
  \uref{https://matklad.github.io/} & GitHub :& \href{https://github.com/matklad}{https://github.com/matklad} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Saint Petersburg Academic University}{St. Petersburg, Russia}
      {Masters of Software Engineering, unfinished}{2014 -- 2016}
    \resumeSubheading
      {Saint Petersburg State University}{St. Petersburg, Russia}
      {Specialist of Software Engineering}{2009 -- 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rust programming language (voluntary work)}{}
      {Cargo team}{2017 - Present}
      \resumeItemListStart
      Cargo is a package manager/build tool for the Rust programming
      language. As a member of Cargo team, I've done significant
      implementation work, notably in the area of IDE integration,
      some design work and a lot of mentoring for new contributors.
      \resumeItemListEnd

    \resumeSubheading
      {JetBrains}{St. Petersburg, Russia}
      {Software Engineer}{Oct 2016 - Jan 2018}
      \resumeItemListStart
        \resumeItem{IntelliJ Rust}
          {is a plugin for the Rust programming language for IntelliJ
            IDEA. It does not use the Rust Language Server, and
            instead has its own Rust compiler frontend in Kotlin. I've
            lead the project development and am still the contributor
            with the largest number of commits. I've done low-level
            language work (parsing, name resolution, type inference,
            initial macro expansion), mid-level integration between
            IDE and Cargo (on both sides), high-level user-visible
            features and GUIs and maintained documentation for users
            and developers of the plugin. I've also made the project
            open and accessible for outside contributors and, as a
            result, current maintainers of the plugin started with a
            pull request, and then were hired by
            JetBrains.
          }
        \resumeItem{Kotlin Native:}
          {implementation work on the CLion plugin and debugger support}
      \resumeItemListEnd

    \resumeSubheading
      {JetBrains}{St. Petersburg, Russia}
      {Software Engineer}{2012 -- 2014}
      \resumeItemListStart
        \resumeItem{Stepik.org}
          {is an e-learning platform written in Python. I was
            responsible for various backend subsystems. Most notably,
            I've implemented the exercises subsystem, including the
            sandbox environment for executing untrusted code.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Open Source Projects}
  \resumeSubHeadingListStart
  \resumeSubheading
      {IntelliJ Rust}{}
      {\uref{https://github.com/intellij-rust/intellij-rust}}{}
      \resumeItemListStart
      \resumeItemListEnd

  \resumeSubheading
      {Fall}{}
      {\uref{https://github.com/matklad/fall}}{}
      \resumeItemListStart
      An experimental parser generator, geared towards IDE requirements.
      \resumeItemListEnd
      
  \resumeSubheading
      {Tom}{}
      {\uref{https://github.com/matklad/tom}}{}
      \resumeItemListStart
      A format preserving parser/editor for TOML documents.
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{document}
